### 2021-04-23 final-report.latex/conclusion.tex
Final draft

In the $\phi^4$ model, we verified a phase transition at $m_0^2=-0.72$ using the magnitude of the average magnetization, the magnetic susceptibility, the Binder cumulant and the bimodality. This process verified the effectiveness of the Monte Carlo computational system. We then generalized our system to the $O(3)$ non-linear sigma model and transitioned to a \texttt{C++} code base. We confirmed our calculations with known results by measuring the internal energy and magnetic susceptibility. We calculated the topological susceptibility $\chi_t$ to analyze its divergence in the continuum limit, confirming that this is indeed the case even at finite flow time. Specifically, the topological susceptibility under the gradient flow follows either a power-law relationship or a logarithmic relationship as a function of lattice size, both of which diverge as $L\rightarrow\infty$.  At flow time $\tau=5t_0$, the $\chi^2/DOF$ goodness of fit values are of \powchi and \logchi respectively.

Finally, we demonstrated the relationship between the topological charge and the $\theta$ in the topological action. This plot demonstrates quantitatively the different divergences of the topological susceptibility, which is equivalent to the slope at $\theta=0$. In the $\tau=0$ case, we see the slope rapidly approach positive infinity at $\theta=0$. While this transition occurs more slowly with the application of the gradient flow, the slope continues to increase.

Though the logarithmic and power-law functions visually fit the susceptibility data well, the $\chi_2$ values are high. This imprecision can be attributed to underestimated errors. Since the $\tau=0$ case features a more acceptable fit ($\chi^2/DOF=1.8$ for the power-law), the gradient flow seemingly contributes to this error. While the Jackknife method accurately estimates statistical errors of the sample, we did not incorporate any systematic errors arising from the gradient flow calculation. Future work could reduce the tolerance of the adaptive step size algorithm to make this calculation more accurate, though this increases computational requirements substantially. Furthermore, a larger number of lattice sizes may provide a more complete picture of the continuum limit.

@@

Generally, this study has implications in both condensed matter and nuclear physics as the NLSM is used in both. Though the calculation of the $\chi_t$ divergence confirms existing literature, the relationship between the topological charge and $\theta$ in the flow time was previously unexplored. Beyond the convergence of $\chi_t$, this relationship has applications in condensed matter where different values of $\theta$ can describe spin-chains of fermions and bosons \cite{bogli2012}. Furthermore, the mass gap has a strong relationship with the $\theta$-terms in topological NLSM, featuring massive and massless regimes \cite{allessalom2008}.

>>>>

In the $\phi^4$ model, we verified a phase transition at $m_0^2=-0.7$ using the magnitude of the average magnetization, the magnetic susceptibility, the Binder cumulant and the bimodality. This process verified the effectiveness of the Monte Carlo computational system. We then generalized our system to the $O(3)$ non-linear sigma model and transitioned to a C++ code base. We confirmed our calculations with known results by measuring the internal energy and magnetic susceptibility. We calculated the topological susceptibility $\chi_t$ to analyze its divergence in the continuum limit, confirming that this is indeed the case even at finite flow time. Specifically, the topological susceptibility under the gradient flow follows either a power law relationship or a logarithmic relationship as a function of lattice size, both of which diverge as $L\rightarrow\infty$.  At flow time $\tau=5t_0$, the $\chi^2/DOF$ goodness of fit values are of \powchi and \logchi respectively.

Finally, we demonstrated the relationship between the topological charge and the $\theta$ in the topological action. This plot demonstrates quantitatively the different rates of divergence in the topological susceptibility. In the $\tau=0$ case, we see the slope rapidly approach positive infinity at $\theta=0$. While this transition occurs more slowly with the application of the gradient flow, the slope continues to increase.

Though the logarithmic and power-law functions visually fit the susceptibility data well, the $\chi^2$ values are high. This imprecision can be attributed to underestimated errors. Since the $\tau=0$ case features a more acceptable fit ($\chi^2/DOF=1.8$ for the power-law), the gradient flow seemingly contributes to this error. While the Jackknife method accurately estimates statistical errors of the sample, we did not incorporate any systematic errors arising from the gradient flow calculation. Future work could reduce the tolerance of the adaptive step size algorithm to make this calculation more accurate, though this change increases computational requirements substantially. Furthermore, a larger number of lattice sizes may provide a more complete picture of the continuum limit.

@@

Generally, this study has implications in both condensed matter and nuclear physics. Though the calculation of the $\chi_t$ divergence confirms existing literature, the relationship between the topological charge and $\theta$ in the flow time was previously unexplored. Beyond the convergence of $\chi_t$, this relationship has applications in condensed matter where different values of $\theta$ can describe spin-chains of either fermions or bosons \cite{bogli2012}. Furthermore, the mass gap has a strong relationship with the $\theta$-term in the topological NLSM, featuring massive and massless regimes \cite{allessalom2008}.

### 2021-04-23 final-report.latex/intro.tex
Final draft

Quantum field theory (QFT) is an framework used to describe a range of physical phenomena to a remarkable degree of accuracy. Paired with the Standard Model, QFT provides the prevailing basis for all small-scale physics (that is, where general relativity does not apply) and is the fundamental tool for studying particle physics. QFT also plays a critical role in condensed matter physics through effective field theories which model emergent phenomena such as phonons and quasiparticles. Compared to experiment, QFT is remarkably accurate, famously predicting the electron $g$-factor to eleven significant figures \cite{odom2006}, arguably the most accurate prediction in all of science.

@@

One such example is the \textit{non-linear sigma model} (NLSM), a prototypical theory in both condensed matter and particle physics. In solid-state systems, this model describes Heisenberg ferromagnets \cite{callan1985} and in nuclear physics, it acts as a prototype for quantum chromodynamics (QCD), the gauge theory that describes the strong nuclear force. In general, the NLSM shares key features with non-Abelian gauge theories such as QCD, including a mass gap and asymptotic freedom \cite{polyakov1975}. Therefore, the NLSM is a useful model for exploring the effect of these properties using a simpler system.

In this study, we specifically consider the $O(3)$ non-linear sigma model in $1+1$ dimensions (one dimension of space, one dimension of time). This theory exhibits topological properties such as \textit{instantons}, or classical field solutions at local minima of the action in Euclidean space. Solutions such as these are ``topologically protected,'' meaning they cannot evolve into the vacuum state via small fluctuations. Therefore, it is critically important to take topology into account when considering quantum field theories in a cosmology and high energy physics \cite{goddard1986}. Additionally, topological stability may become a key tool for fault-tolerant quantum computers \cite{kitaev1997}. In these devices, topology could protect the delicate quantum states necessary for information processing.

Since the NLSM in not perturbatively renormalizable, we require nonperturbative techniques to study topological effects. An alternative solution is to place the field on a discretized Euclidean lattice, a technique originally used for quantum chromodynamics \cite{wilson1974}. After this transformation, fields become computationally calculable. This process introduces the lattice spacing as a length scale $a$ where the \textit{continuum limit} is defined as taking $a$ to zero. We expect physical observables to converge in the continuum limit, however this is not always the case. As an example, states of definite angular momentum mix when discretized on a rectangular lattice due to a breaking of continuous rotational symmetry. This causes some operators that depend on angular momentum to suffer divergences.

In this study, we focus on one observable that diverges in the continuum: the topological susceptibility. The topological susceptibility in the 1+1 $O(3)$ NLSM has been the subject of debate for the past four decades \cite{bietenholz2018} since it is unclear if a convergent solution exists. While the some analytical arguments argue the topological susceptibility should approach zero in the continuum limit, numerical results predict infinities. In QCD, mathematical techniques proved that the susceptibility vanishes in the continuum limit \cite{giusti2004}, a fact supported by numerical calculation \cite{giusti2004}.

To remedy this issue, we consider the gradient flow, a technique designed to remove divergences in operators. By dampening high-frequency fluctuations, the gradient flow reduces terms which scale with the inverse lattice spacing, making some observables finite on the lattice \cite{monahan2016}. In QCD, the gradient flow successfully makes the topological susceptibility finite in numerical calculations \cite{bruno2014}, corroborating the analytical result in \cite{giusti2004}. This success has motivated the usage of the gradient flow to calculate the topological susceptibility in the 1+1 $O(3)$ NLSM, though the observable still diverges in the continuum limit \cite{bietenholz2018}.

@@

To numerically study the topological qualities of the non-linear sigma model, we first implement a Markov chain Monte Carlo simulation. We initially construct a proof-of-concept Python program that models the simpler $\phi^4$ model (see Sec.~\ref{sec:phi4}). After comparing with existing literature, we transition to a C++ simulation for efficiency, implementing the non-linear sigma model in larger lattices. Since the gradient flow has no exact solution in the non-linear sigma model, we implement a numerical solution using a fourth-order Runge-Kutta approximation with automatic step sized. By applying the gradient flow to every configuration in the sample, we can measure its effect on the topological charge and susceptibility.

@@

A portion of this work began during the summer of 2021 using funding from the 1693 Scholars Program. This preliminary research consisted of literature review and numerical tests with an Ising model simulation as well as an initial implementation of the $\phi^4$ model. The $\phi^4$ calculation performed in this study and the entirety of the NLSM portion occurred during the academic year as part of the PHYS 495/496 Honors course.

\section{Conventions}
\begin{itemize}
    \item Throughout this paper, we use natural units, i.e. $\hbar = 1$ and $c=1$.
    \item We use Einstein summation notation, an implicit sum over repeated spacetime indices. For example, if $x^\mu$ is a spacetime four-vector and $x_\mu$ is its covariant form, the term
        \begin{align*}
            x^\mu x_\mu &= \sum^4_{\mu=0} x^\mu x_\mu \\
            &= x_0^2-x_1^2-x_2^2-x_3^2.
        \end{align*}
\end{itemize}

>>>>

Quantum field theory (QFT) is a framework used to describe a range of physical phenomena to a remarkable degree of accuracy. Paired with the Standard Model, QFT provides the prevailing basis for all small-scale physics (that is, where general relativity does not apply) and is the fundamental tool for studying particle physics. QFT also plays a critical role in condensed matter physics through effective field theories which model emergent phenomena such as phonons and quasiparticles. Compared to experiment, QFT is remarkably accurate, famously predicting the electron $g$-factor to eleven significant figures \cite{odom2006}, arguably the most accurate prediction in all of science.

@@

One such example is the \textit{non-linear sigma model} (NLSM), a prototypical theory in both condensed matter and particle physics. In solid-state systems, this model describes Heisenberg ferromagnets \cite{callan1985} and in nuclear physics, it acts as a prototype for quantum chromodynamics (QCD), the gauge theory that describes the strong nuclear force. In general, the NLSM shares key features with non-Abelian gauge theories such as QCD, including a mass gap and asymptotic freedom \cite{polyakov1975}. Therefore, the NLSM is a useful model for exploring the effect of these properties in a simpler system.

In this study, we specifically consider the $O(3)$ NLSM in 1+1 dimensions (one dimension of space, one dimension of time). This theory exhibits topological properties such as \textit{instantons}, or classical field solutions at local minima of the action in Euclidean space. Solutions such as these are ``topologically protected'', meaning they cannot evolve into the vacuum state via small fluctuations. Due to this property, topology is critically important to quantum field theories in cosmology and high energy physics \cite{goddard1986}. Additionally, topological stability may become a key tool for fault-tolerant quantum computers \cite{kitaev1997}. In these devices, topology protects the delicate quantum states necessary for information processing.

Since the NLSM in not perturbatively renormalizable, we require nonperturbative techniques to study topological effects. A solution is to place the field on a discretized Euclidean lattice, a technique originally used for quantum chromodynamics \cite{wilson1974}. After this transformation, fields become numerically calculable using modern computers. This process introduces the lattice spacing as a length scale $a$ where the \textit{continuum limit} is defined as taking $a$ to zero. We expect physical observables to converge in the continuum limit, however this is not always the case. As an example, states of definite angular momentum mix when discretized on a rectangular lattice due to a breaking of continuous rotational symmetry. This causes some operators that depend on angular momentum to suffer divergences.

In this study, we focus on one observable that diverges in the continuum: the topological susceptibility. The topological susceptibility in the 1+1 $O(3)$ NLSM has been the subject of debate for the past four decades \cite{bietenholz2018} since it is unclear if a convergent solution exists. While the some analytical arguments argue the topological susceptibility should approach zero in the continuum limit, numerical results predict infinities \cite{berg1981}. In QCD, mathematical techniques proved that the susceptibility vanishes in the continuum limit \cite{giusti2004}, a fact supported by numerical calculation \cite{bruno2014}.

To remedy this issue, we consider the gradient flow, a technique designed to remove divergences in operators. By dampening high-frequency fluctuations, the gradient flow reduces terms that scale with the inverse lattice spacing, making some observables finite on the lattice \cite{monahan2016}. In QCD, the gradient flow successfully makes the topological susceptibility finite in numerical calculations \cite{bruno2014}, corroborating the analytical result in \cite{giusti2004}. This success has motivated the usage of the gradient flow to calculate the topological susceptibility in the 1+1 $O(3)$ NLSM, though recent studies demonstrate that the observable still diverges in the continuum limit \cite{bietenholz2018}.

@@

To numerically study the topological qualities of the NLSM, we first implement a Markov chain Monte Carlo simulation. We initially construct a proof-of-concept Python program that models the simpler $\phi^4$ model (see Sec.~\ref{sec:phi4}). After comparing with existing literature, we transition to a C++ simulation for efficiency, implementing the NLSM on larger lattices. Since the gradient flow has no exact solution in the NLSM we implement a numerical solution using a fourth-order Runge-Kutta approximation with automatic step sizing. By applying the gradient flow to every configuration in the sample, we can measure its effect on the topological charge and susceptibility.

@@

A portion of this work began during the summer of 2020 using funding from the 1693 Scholars Program. This preliminary research consisted of literature review and numerical tests with an Ising model simulation as well as an initial implementation of the $\phi^4$ model. The $\phi^4$ calculation performed in this study and the entirety of the NLSM portion occurred during the academic year as part of the PHYS 495/496 Honors course.

\section{Conventions}
\begin{itemize}
    \item Throughout this paper, we use natural units, i.e. $\hbar = 1$ and $c=1$.
    \item We use Einstein summation notation, an implicit sum over repeated spacetime indices. For example, if $x^\mu$ is a four-vector in Minkowski spacetime and $x_\mu$ is its covariant form, the term
        \begin{align*}
            x^\mu x_\mu &= \sum^4_{\mu=0} x^\mu x_\mu \\
            &= x_0^2-x_1^2-x_2^2-x_3^2.
        \end{align*}

\end{itemize}

### 2021-04-23 final-report.latex/main.tex
Final draft

\documentclass[12pt]{report}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
%\usepackage[%
    %style=numeric, 
    %sorting=none,
    %doi=false,
    %url=false,
    %giveninits=true,
    %eprint=false,
    %isbn=false,
    %clearlang=true,
    %date=year,
    %hyperref]{biblatex}
\usepackage[style=phys,biblabel=brackets,maxbibnames=3]{biblatex}
%\renewbibmacro{in:}{%
  %\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}

@@

\pagenumbering{roman}
\tableofcontents
\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\paragraph
\indent I would like to thank my advisor, Prof. Christopher Monahan. His constant helpfulness has made this research possible and enjoyable. I would also like to thank the entire faculty of the William \& Mary Physics Department. The amount of knowledge and wisdom they have bestowed upon me has been beyond my imagination.

I also acknowledge the help the High Performance Computing group at William \& Mary, whose cluster performed many of these simulations. And finally, I would like to acknowledge the financial help of the 1693 Scholars Program which funded preliminary research over the summer.

@@

\printbibliography

>>>>

\documentclass[12pt]{report}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{tabularx}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
%\usepackage[%
    %style=numeric, 
    %sorting=none,
    %doi=false,
    %url=false,
    %giveninits=true,
    %eprint=false,
    %isbn=false,
    %clearlang=true,
    %date=year,
    %hyperref]{biblatex}
\usepackage[style=phys,biblabel=brackets,maxbibnames=3]{biblatex}
%\renewbibmacro{in:}{%
  %\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\DefineBibliographyStrings{english}{%
  bibliography = {References},
}

@@

\pagenumbering{roman}
\tableofcontents
\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\paragraph
\indent I would like to thank my advisor, Professor Christopher Monahan. His constant helpfulness has made this research possible and enjoyable. I would also like to thank the entire faculty of the William \& Mary Physics Department. The amount of knowledge and wisdom they have given me has been beyond my imagination.

I would like to acknowledge the help of the High Performance Computing group at William \& Mary, whose cluster performed many of these simulations. I also want to acknowledge the financial help of the 1693 Scholars Program which funded preliminary research over the summer.

Finally, I would like to thank my friends and family who helped me reach this point in my academic and personal journey.

@@

\printbibliography[heading=bibintoc]

### 2021-04-23 final-report.latex/results.tex
Final draft

Using the Monte Carlo procedure outlined in Sec.~\ref{sec:methods}, we run statistical simulations on the $\phi^4$ model and NLSM.
\section{$\phi^4$ results}
We initially implement the $\phi^4$ model to verify the results of our system. According to previous studies \cite{chang1976, monahan2016, schaich2006}, the $\phi^4$ model exhibits a symmetric and broken phase depending on its parameters $m_0^2$ and $\lambda$, specifically occurring at $m_0^2 = -0.72$ when $\lambda = 0.5$. We verify this result by plotting four observables: the lattice average $|\langle\bar\phi\rangle|$, the magnetic susceptibility $\chi$, the Binder cumulant $U$ and the bimodality $B$ in Fig.~\ref{fig:phi4}.
\begin{figure}[h!]
    \centering
      \includegraphics[width=0.9\textwidth]{imgs/phi4.png}
      \caption{\label{fig:phi4} The lattice average $|\langle\bar\phi\rangle|$, the lattice susceptibility $\chi$, the Binder cumulant $U$ and the bimodality $B$ plotted as functions of $m_0^2$. $L=64$, $\lambda=0.5$. The lattice was thermalized from a hot start for 1000 sweeps. Afterwards, 1000 measurements were taken with 50 sweeps between each. The red horizontal line indicates $U=2/3$, the symmetric limit of the Binder cumulant.}
\end{figure}
This figure confirms a phase transition near $m_0^2=-0.72$ and supports the accuracy of our model.

\section{Non-linear sigma model results}
After confirming the phase transition in the $\phi^4$ model, we turn to the NLSM. In order to confirm the accuracy of the model, we compare results with existing literature. We first compare our results to Berg \& L\"uscher \cite{berg1981}, specifically measuring the internal energy and magnetic susceptibility.

@@

We also seek to confirm the results from Bietenholz et al. \cite{bietenholz2018}. Specifically, we show the topological susceptibility $\chi_t$ diverges in the continuum limit even at finite flow time. Since $\chi_t$ is in units of inverse distance squared, we multiply by $\xi_2^2$, the square of the second moment correlation length, to achieve a scale-invariant value $\chi_t\xi_2^2$. Additionally, we use a parameter $t_0$ to scale the flow time such that $t_0\sim L^2$. In our Monte Carlo simulation, we adapt the same values as \cite{bietenholz2018} for $\xi_2$.

@@

      \begin{subfigure}[b]{\textwidth}
          \centering
          \includegraphics[width=0.8\textwidth]{imgs/divergence_flowed.png}
          \caption{$\tau = 5t_0$}
      \end{subfigure}
      \caption{\label{fig:divergence} $\chi_t\xi_2^2$ as a function of $L$. The data is fit with both a logarithmic and power fit. Simulation run with 10,000 measurements, measurements every 50 sweeps, 1,000 sweep thermalization. In the $\tau=0$ case, we have compared our result with the curve fit found in \cite{bietenholz2018}.}
    \end{center}
\end{figure}
The data is fit with two options: a log fit
\begin{equation}
    \chi_t \xi_2^2 = a \mathrm{log}(b L + c)
\end{equation}
and a power law fit
\begin{equation}
    \chi_t \xi_2^2 = A L^B + C.
\end{equation}
We calculate the parameters to these functions using the \texttt{curve\_fit} tool in the \texttt{scipy} Python package \cite{virtanen2020}. When $\tau=5t_0$, the data fits these functions with $\chi^2/DOF$ of \logchi and \powchi respectively, indicating errors were underestimated. Both of these function diverge as $L\rightarrow \infty$, indicating that the topological susceptibility does as well in the continuum limit. Though there is a clear difference between the quantitative fit from \cite{bietenholz2018} and the fit calculated in this work, both demonstrate divergent behavior. This result supports the inherent divergence of $\chi_t$ in the continuum limit.

\subsection{Topological charge when $\theta\neq 0$}
Following the method explained in Sec.~\ref{sec:topotheta}, we calculate the imaginary part of $\langle Q \rangle$ for arbitrary $\theta$. We perform this calculation for four values of the flow time $\tau$, shown in Fig~\ref{fig:theta}.
\begin{figure}[h!]
    \centering
      \includegraphics[width=\textwidth]{imgs/theta.png}
      \caption{\label{fig:theta} Imaginary part of $\langle Q \rangle$ as a function of $\theta$. Simulation run with 10,000 measurements, measurements very 50 sweeps, 1,000 sweep thermalization. Note the different scaling of the $y$-axis.}
\end{figure}
These plots demonstrate the divergence of the continuum limit in the $\tau=0$ and the flowed regimes. In the $\tau=0$ case, the slope increases sharply, reflecting the linear divergence of $\chi_t$. However in the flowed regime, this divergence is much slower, reflecting the logarithmic or power-law relationship shown in Fig.~\ref{fig:bietenholz}.

>>>>

Using the Monte Carlo procedure outlined in Sec.~\ref{sec:methods}, we run statistical simulations on the $\phi^4$ model and NLSM.
\section{$\phi^4$ Results}
We initially implement the $\phi^4$ model to verify the results of our system. According to previous studies \cite{chang1976, monahan2016, schaich2006}, the $\phi^4$ model exhibits a symmetric and broken phase depending on its parameters $m_0^2$ and $\lambda$, transitioning at $m_0^2 = -0.72$ when $\lambda = 0.5$. We verify this result by plotting four observables: the lattice average $|\langle\bar\phi\rangle|$, the magnetic susceptibility $\chi_m$, the Binder cumulant $U$ and the bimodality $B$ in Fig.~\ref{fig:phi4}.
\begin{figure}[h!]
    \centering
      \includegraphics[width=0.9\textwidth]{imgs/phi4.png}
      \caption{\label{fig:phi4} The lattice average $|\langle\bar\phi\rangle|$, the magnetic susceptibility $\chi_m$, the Binder cumulant $U$ and the bimodality $B$ plotted as functions of $m_0^2$. $L=64$, $\lambda=0.5$. The lattice was thermalized from a hot start for 1000 sweeps. Afterwards, 1000 measurements were taken with 50 sweeps between each. The red horizontal line indicates $U=2/3$, the broken phase limit of the Binder cumulant.}
\end{figure}
This figure confirms a phase transition near $m_0^2=-0.7$ and supports the accuracy of our model.

\section{Non-linear Sigma Model Results}
After confirming the phase transition in the $\phi^4$ model, we turn to the NLSM. In order to confirm the accuracy of the model, we compare results with existing literature. We first consider the results of Berg \& L\"uscher \cite{berg1981}, specifically the internal energy and magnetic susceptibility.

@@

We also seek to confirm the results from Bietenholz et al. \cite{bietenholz2018}. Specifically, we show the topological susceptibility $\chi_t$ diverges in the continuum limit even at finite flow time. Since $\chi_t$ is in units of inverse distance squared, we multiply by $\xi_2^2$, the square of the second moment correlation length, to achieve a scale-invariant value $\chi_t\xi_2^2$. Additionally, we use a parameter $t_0$ to scale the flow time such that $t_0\sim L^2$. In our Monte Carlo simulation, we utilize the same values as \cite{bietenholz2018} for $\xi_2$, $\beta$ and $t_0$.

@@

      \begin{subfigure}[b]{\textwidth}
          \centering
          \includegraphics[width=0.8\textwidth]{imgs/divergence_flowed.png}
          \caption{$\tau = 5t_0$}
      \end{subfigure}
      \caption{\label{fig:divergence} $\chi_t\xi_2^2$ as a function of $L$. We fit the data with both a logarithmic and power fit. Simulation run with 10,000 measurements, once every 50 sweeps, 1,000 sweep thermalization. In the $\tau=0$ case, we have compared our result with the curve fit found in \cite{bietenholz2018}.}
    \end{center}
\end{figure}
We fit the data with two options: a log fit
\begin{equation}
    \chi_t \xi_2^2 = a \mathrm{log}(b L + c)
\end{equation}
and a power law fit
\begin{equation}
    \chi_t \xi_2^2 = a L^b + c.
\end{equation}
We calculate the parameters to these functions using the \texttt{curve\_fit} tool in the \texttt{scipy} Python package \cite{virtanen2020}. When $\tau=5t_0$, the data fits these functions with $\chi^2/DOF$ of \logchi and \powchi respectively, indicating errors were underestimated. Both of these functions diverge as $L\rightarrow \infty$, indicating that the topological susceptibility also diverges in the continuum limit. Though there is a clear difference between the quantitative fit from \cite{bietenholz2018} and the fit calculated in this work, both demonstrate divergent behavior. This result supports the inherent divergence of $\chi_t$ in the continuum limit.

\subsection{Topological Charge when $\theta\neq 0$}

Following the method explained in Sec.~\ref{sec:topotheta}, we calculate the imaginary part of $\langle Q \rangle$ for arbitrary $\theta$. We perform this calculation for three values of the flow time $\tau$, shown in Fig~\ref{fig:theta}.
\begin{figure}[h!]
    \centering
      \includegraphics[width=\textwidth]{imgs/theta.png}
      \caption{\label{fig:theta} Imaginary part of $\langle Q \rangle$ as a function of $\theta$. Simulation run with 10,000 measurements, measurements very 50 sweeps, 1,000 sweep thermalization. Note the different scaling of the $y$-axis.}
\end{figure}
These plots demonstrate the divergence of the continuum limit in the $\tau=0$ and the flowed regimes. In the $\tau=0$ case, the slope increases sharply, reflecting the rapid divergence of $\chi_t$. However in the flowed regime, this divergence is much slower, reflecting the decreased values of $\chi_t$ shown in Fig.~\ref{fig:bietenholz}.
